In the Crucible: Massive Compact Galaxies with High-Velocity Outflows and Eddington-Limited Star Formation

### 2012-04-17 trunk/tex/sigmasfr/ms.tex
updates to section 2.2

We use the method of \citet{mou11} to derive stellar masses and
UV-based SFRs from fits to the 0.1--5~$\mu$m SEDs.  We also estimate
IR-based SFRs from the 12~$\mu$m and 22~$\mu$m WISE photometry.

Comment on agreement between SFR indicators.

@@

@@

@@

@@

@@

>>>>

We estimate IR-based star-formation rates for the 25/29 galaxies with
WISE 12~$\mu$m detections by fitting \citet{cha01} templates to their
12 and 22~$\mu$m fluxes.  For the 14/29 galaxies with 22~$\mu$m
detections, the method of \citet{ruj12} yields SFRs that agree with
the above values within 0.05~dex.  We note that the shape of the IR
SED for star-forming galaxies depends on the surface density of star
formation \citep[e.g.,][]{ruj11,elb11}, with more compact starbursts
having larger total-IR (8--1000~$\mu$m) to mid-IR (8--24~$\mu$m)
ratios.  The extreme $\sigmasfr$ values of our sample imply large
total-IR to mid-IR ratios, characteristic of the most luminous
galaxies in the local universe \citep[e.g.,][]{cha01,dal02,rie09}.
For the 8/29 sources where we estimate $SFR_{IR}>200$~\msun~yr$^{-1}$
above, using the most luminous local templates would yield SFRs that
are larger by 0.5~dex.

We also estimate star-formation rates and stellar masses based on
stellar population fits to the $\lrest=0.1$--3~$\mu$m SEDs using the
method of \citet{mou11}.  For galaxies with
$SFR_{IR}>50$~\msun~yr$^{-1}$, there is agreement between these
UV-optical-based estimates and $SFR_{IR}$ with a scatter of 0.32~dex.

@@

\bibitem[Chary \& Elbaz(2001)]{cha01} Chary, R., \& Elbaz, D.\ 2001,
  \apj, 556, 562

@@

\bibitem[Dale \& Helou(2002)]{dal02} Dale, D.~A., \& Helou, G.\ 2002,
  \apj, 576, 159

@@

\bibitem[Elbaz et al.(2011)]{elb11} Elbaz, D., Dickinson, M., Hwang,
  H.~S., et al.\ 2011, \aap, 533, A119

@@

\bibitem[Rieke et al.(2009)]{rie09} Rieke, G.~H., Alonso-Herrero, A.,
  Weiner, B.~J., et al.\ 2009, \apj, 692, 556

@@

\bibitem[Rujopakarn et al.(2011)]{ruj11} Rujopakarn, W.,
  Rieke, G.~H., Eisenstein, D.~J., \& Juneau, S.\ 2011, \apj, 726, 93
\bibitem[Rujopakarn et al.(2012)]{ruj12} Rujopakarn, W., Rieke, G.~H.,
  Weiner, B.~J., et al.\ 2011, arXiv:1107.2921
